---
title: Exploring [PGA ShotLink](https://www.pgatour.com/stats/shotlinkintelligence/overview.html)
output: 
  github_document:
    html_preview: true
    toc: true
    
---

Take a look at the data

Three data sets

check out stroke level

```{r, message=FALSE}

library(tidyverse)

stroke_level_import = read.delim(file = "data/sample_download/StrokeLevelTOURChamp.txt")

stroke_level_import %>% 
  str()

```

Cool data, want to fix column names

```{r, message=FALSE}


library(janitor)

stroke_level_clean_names = stroke_level_import %>% 
  clean_names()


stroke_level_clean_names %>% 
  colnames()


```

Convert coordinates to numbers

```{r, message=FALSE}

stroke_level_num_coords = stroke_level_clean_names %>% 
  mutate(x = str_replace_all(string = x_coordinate,
                             pattern = ",",
                             replacement = "")) %>%
  mutate(y = str_replace_all(string = y_coordinate,
                             pattern = ",",
                             replacement = "")) %>% 
  mutate(z = str_replace_all(string = z_coordinate,
                             pattern = ",",
                             replacement = "")) %>% 
  mutate(x = as.numeric(x),
         y = as.numeric(y),
         z = as.numeric(z)) %>% 
  select(-x_coordinate, 
         -y_coordinate, 
         -z_coordinate)

stroke_level_num_coords %>% 
  select(x,y,z) %>% 
  as_tibble() %>% 
  head(20)


```

Notice that there are zeros, want to take a look at the data, 

```{r, message=FALSE}

stroke_level_num_coords %>% 
  mutate(hole = factor(hole, ordered = T)) %>% 
  ggplot(mapping = aes(x = x,
                       y = y,
                       color = hole)) +
  geom_point() +
  coord_equal(clip = "off") +
  theme()


```


Really encouraging except for the zeros


```{r, message=FALSE}

n_zeros = stroke_level_num_coords %>% 
  filter(x == 0) %>% 
  as.data.frame() %>% 
  nrow()

n_zeros/nrow(stroke_level_num_coords)

```

What are the zeros?

```{r, message=FALSE}

stroke_level_num_coords %>% 
  select(round,
         hole,
         player,
         shot,
         x) %>% 
  arrange(round,
          hole,
          player,
          shot) %>% 
  as.data.frame() %>% 
  head(25)

```

These are shots that finish in the hole, READ THE DOCS, convert to NAs

```{r, message=FALSE}

stroke_level_no_zeros = stroke_level_num_coords %>% 
  mutate(x = ifelse(x == 0,NA,x)) %>% 
  mutate(y = ifelse(y == 0,NA,y)) %>% 
  mutate(z = ifelse(z == 0,NA,z)) 

```


Plot it again

```{r, message=FALSE}

stroke_level_no_zeros %>% 
  mutate(hole = factor(hole, ordered = T)) %>%
  ggplot(mapping = aes(x = x,
                       y = y,
                       color = hole)) +
  geom_point() +
  coord_equal(clip = "off") +
  theme()


```



Plot the cut

```{r, message=FALSE}

stroke_level_no_zeros %>% 
  group_by(to_location_scorer,
           to_location_laser) %>% 
  summarize(shots = n()) %>% 
  as.data.frame() %>% 
  arrange(to_location_scorer,
          to_location_laser)

```


```{r, message=FALSE}

stroke_level_with_cut = stroke_level_no_zeros %>% 
  mutate(result_cut = case_when(to_location_scorer == 'Fairway' ~ 'fairway',
                                to_location_scorer %in% c('Fairway Bunker', 'Green Side Bunker') ~ 'bunker',
                                to_location_scorer %in% c('Intermediate Rough','Primary Rough') ~ 'rough',
                                to_location_scorer == 'Green' ~ 'green',
                                is.na(x) ~ 'hole',
                                T ~ 'other'))


stroke_level_with_cut$result_cut %>% 
  table()

```



```{r, message=FALSE}

stroke_level_with_cut %>% 
  ggplot(mapping = aes(x = x,
                       y = y,
                       color = result_cut)) +
  geom_point()

```

```{r, message=FALSE}

result_cut_colors = c('bunker'='tan',
                      'fairway'='green',
                      'green'='lightgreen',
                      'rough'='darkgreen',
                      'other'='red')


stroke_level_with_cut %>% 
  ggplot(mapping = aes(x = x,
                       y = y,
                       color = result_cut)) +
  geom_point() +
  scale_color_manual(values = result_cut_colors) +
  coord_equal()

```


```{r, message=FALSE}

stroke_level_with_cut %>% 
  filter(hole == 1) %>% 
  ggplot(mapping = aes(x = x,
                       y = y,
                       color = result_cut)) +
  geom_point() +
  scale_color_manual(values = result_cut_colors) +
  coord_equal()

```

Going to add these cleaning steps to a function



